%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Dewesh Agrawal
\documentclass[hidelinks,margin,line,10pt,a4paper]{resume}
\usepackage{hyperref}

%______________________________________________________________________________________________________________________
\begin{document}


\textbf{\begin{huge}\hspace{-28mm}Dewesh Agrawal\end{huge}}	\hfill\vspace{0mm} C-329, Azad Hall
\vspace{0mm}\\\vspace{0mm}%
\hfill IIT Kharagpur
\vspace{0mm}\\\vspace{0mm}%
\hspace{-25mm}\hspace{-4mm} Senior Year Undergraduate Student, Roll Number - 10CS30018		\hfill West Bengal - 721302, India
\vspace{0mm}\\\vspace{0mm}%
\hspace{-25mm}\hspace{-4mm} Department of Computer Science and Engineering	\hfill Mobile: +91 9474828361
\vspace{0mm}\\\vspace{0mm}%
\hspace{-25mm} \hspace{-4mm}Indian Institute of Technology, Kharagpur \hfill Email : deweshiitkgp@gmail.com


\begin{resume}
%__________________________________________________________________________________________________________________
% Education

\section{\mysidestyle Education}
%\vspace{5mm}%
\begin{list2}

            \item \textbf{Indian Institute of Technology, Kharagpur} \hfill Kharagpur, India \vspace{0mm}\\\vspace{1mm}%
    		Bachelor of Technology, Department of Computer Science and Engineering \hfill 2010 -- 2015  \vspace{-1mm}\\\vspace{1mm}%
		CGPA: 8.23/10 {(after 8 semesters)}
		 
             \item \textbf{K.B.R. College } \hfill Cuttuck, India \vspace{0mm}\\\vspace{1mm}%
    		{Class XII, Council of Higher Secondary Education, Odisha } \hfill { 2009}  \vspace{-1mm}\\\vspace{1mm}%
		{Performance: 82.66\%}
		
			\item \textbf{S.S.V.M. Saintala} \hfill Bolangir, India \vspace{0mm}\\\vspace{1mm}%
    		{Class X, Board of Secondary Education, Odisha } \hfill { 2007 }  \vspace{-1mm}\\\vspace{1mm}%
		{Performance: 90.13\%}
% 


\end{list2}


    %__________________________________________________________________________________________________________________
    %  Relevant Coursework

    \section{\mysidestyle Relevant Courses} 
Algorithm I \& II, Computer Graphics, Image Processing, Computational Geometry, Computational Number Theory, Artificial Intelligence, Information Retrieval, Speech and Natural Language Processing, Compilers, Operating Systems, Database Management Systems, Computer Networks, Software Engineering, Cryptography, Object Oriented System Design, Advanced Graph Theory.

    %__________________________________________________________________________________________________________________
    % Projects
    \section{\mysidestyle Summer Internship}

Title: \textbf{\emph{PDF Editor Prototype Development }} \hfill May-July 2014 \\
ARC document solutions, Kolkata, India \\
Mentor: Dr. Prasenjeet Mandal
\vspace{2mm}%
\begin{itemize}
\item Studied the pdf file specification and the libraries available to parse pdf files.
\item Extended the PDF viewer engine to upport annotationand developed modules for embedding and rendering 3D files in the pdf.
\end{itemize}

Title: \textbf{\emph{User Compensation Admin Tools Development }} \hfill May-July 2013 \\
Electronic Arts Inc., Hyderabad, India \\
Mentor: Mr. S.V. Reddy
\vspace{2mm}%
\begin{itemize}
\item Worked at all play studio and developed administration tools for the mobile game, Monopoly Hotels to compensate users’ loss of data. 
\end{itemize}


Title: \textbf{\emph{Android Game Development and Engine Review }} \hfill May-June 2012 \\
InoxApps, Delhi, India \\
Mentor: Mr. Rachit Jain
\vspace{2mm}%
\begin{itemize}
\item Coded two games, one based on Super Mario and another on flying a helicopter through obstacles for Android OS and Html 5.
\end{itemize}

    \section{\mysidestyle Projects}

Title: \textbf{\emph {Image Searching in PDF }} \hfill May 2014 - Present \\ Indian Institute of Technology Kharagpur \hfill (Masters Thesis Project) \\
Guide: Prof. Partha Bhowmick
\vspace{2mm}%
\begin{itemize}
\item Working on development and design of a system to search relevant images in a pdf file.
\end{itemize}


Title: \textbf{\emph {A New Method for Image Stitching }} \hfill July 2013 - April-2014 \\ Indian Institute of Technology Kharagpur \hfill (Bachelor Thesis Project) \\
Guide: Prof. Partha Bhowmick
\vspace{2mm}%
\begin{itemize}
\item Developed and designed of a new strategy for image stitching using the bending neture of curves.
\end{itemize}

Title: \textbf{\emph {Citation Profiling For physics papers }} \hfill July 2014 - Present \\ Indian Institute of Technology Kharagpur 
\vspace{2mm}%
\begin{itemize}
\item Working profiling the millions of physics papers collected to profile the citation to see the relevance of their nature and its impact on H and I index.
\end{itemize}

Title: \textbf{\emph {3D Pool Game }} \hfill march 2014 - April 2014\\ Indian Institute of Technology Kharagpur \hfill (Term Project)
\vspace{2mm}%
\begin{itemize}
\item Created a 2 player 3D Pool game using OpenGL and made a 3d collision simulator module for the same.
\end{itemize}


Title: \textbf{\emph{Learning Latent Personas From Movie Summary}} \hfill Aug - Novl 2013 \\
Indian Institute of Technology Kharagpur \hfill (Term Project) \\
Guide: Prof. Sudeshna Sarkar
\vspace{2mm}%
\begin{itemize}
\item Made a automated learning system which takes a movie name and looks for wikipedia summery to find out the good characters and the bad characters in the movie. 
\end{itemize}

Title: \textbf{\emph{Online Judge for Algorithmic Problems}} \hfill March - April 2013 \\
Indian Institute of Technology Kharagpur \hfill (Term Project) \\
Guide: Prof. Pabitra Mitra
\vspace{2mm}%
\begin{itemize}
\item Developed a web – based application for automated evaluation of computer programs written in
C/C++/Java. The application takes submission from user as a solution to some problem and complies and
executes on local system and show the result to the user.
\end{itemize}

Title: \textbf{\emph{Facebook Timeline Search Application}}\hfill January - February 2013 \\
Indian Institute of Technology Kharagpur \hfill  (Term Project) \\
Guide: Prof. Pabitra Mitra
\vspace{2mm}%
\begin{itemize}
\item Developed a web based application using Facebook API, which provides search feature to
user for their Facebook timeline. 
\item User can search posts, comments, likes, videos and photos for any particular word in any time limits.
\end{itemize}

Title: \textbf{\emph{Path Planning for Emergency Situation}} \hfill Feb 2013 \\
Hack You, 2013
\vspace{2mm}%
\begin{itemize}
\item Using Google maps api and foursquare api for rating information of places and deciding the 
best possible path in case of a panic situation. 
\end{itemize}


Title: \textbf{\emph {Voice controlled file browser }} \hfill Feb 2012 \\ Indian Institute of Technology Kharagpur \hfill (Inter Hall Opensoft) 
\vspace{2mm}%
\begin{itemize}
\item A file browser controlled totally by voice input from the user, coded in c\# using the Microsoft speech library. 
\end{itemize}
\iffalse
Title: \textbf{\emph{Automation of HMC Bookkeeping Activity}} \hfill Feb-March 2012 \\
Indian Institute of Technology Kharagpur \hfill (Term Project)  \\
Guide: Prof. R. Mall
\vspace{2mm}%
\begin{itemize}
\item Developed a book keeping software for hall management centre, IIT Kharagpur
\item Applications involved User Authentication, registering new students, Allorting Halls and rooms, Distrubuting Funds to Halls, Imposing fines on students, Total Due management, Employee information and duties.
\end{itemize}


Title: \textbf{\emph{Snakes and Ladders Game}} \hfill Feb 2012 \\
Indian Institute of Technology Kharagpur \hfill (Term Project)  \\
Guide: Prof. R. Mall
\vspace{2mm}%
\begin{itemize}
\item Implemented the features of multiplayer and lan play with an option of variable board size, manual and automatic board creation feature for the famous board Game.
\end{itemize}
\fi

% add the snake and ladder in java and risc processor project

    %__________________________________________________________________________________________________________________
    %  Skills
    \section{\mysidestyle Skills} 

\begin{list2}
\item Operating Systems: Windows, Linux(Ubuntu)\vspace{1mm}%
\item Programming Languages: C, C++, Java, Python and PHP \vspace{1mm}%
\item Database Languages: SQL (SQLite, MySQL)\vspace{1mm}%
\item Development Environments: Netbeans, Eclipse, Microsoft Visual Studio.\vspace{1mm}%
\item Designing Softwares: Photoshop, 3d's-Max, Blender , AutoCAD\vspace{1mm}%
\item Library and frameworks : OpenCV, OpenGL, SlimDX, LibGdx\vspace{1mm}%
\end{list2}


    %__________________________________________________________________________________________________________________
    %  Positions of responsibility
    
\section{\mysidestyle Positions of Responsibility} 

\begin{list2}
\item 	Teaching Assistant, Natural language Processing  \hfill Autumn-2014\vspace{1mm}%
\begin{itemize}\vspace{-0.5em}
\renewcommand\labelitemi{--}
\item Was assigned teaching assistant for Dr. Pawan Goyel and helped him in smooth running of the course.
\end{itemize}

\item 	Head, Robotix Winter Workshop,  \hfill Dec-2011\vspace{1mm}%
\begin{itemize}\vspace{-0.5em}
\renewcommand\labelitemi{--}
\item Headed a group of 10 students to successfully complete the project Allegiance.
\end{itemize}

\item 	Member of Bitwise organising and publicity team\hfill 2012\vspace{1mm}%

\begin{itemize}\vspace{-0.5em}
\renewcommand\labelitemi{--}
\item Designed logo, template of website, brochure for Bitwise 2011 attracting 5200 participants from 80 countries and resulting total grant of more than \$4000 from our sponsors. 
\end{itemize}

\end{list2}

%\section{\mysidestyle Academic Achievements}
%\begin {list2}
%\item More than 99.5 percentile in India in the Joint Entrance Examination 2010. \vspace{1mm}%
%\item More than 99.5 percentile in India in All India Engineering Entrance Examination, 2010. ( Odisha state rank : 4 ) \vspace{1mm}%
%\item Ranked 35 in Orissa JEE.  \vspace{1mm}%
%\item Honoured with the award for the best academic performance for the year 2010 by Yuva Manch .\vspace{1mm}%
%\item Nominated for the Medhavi Chhatra Protsahan Pariyojna (MCPP), 2010 for excellent perfomance in 10th Board. %\vspace{1mm}%
%\item Secured the $1^{st}$ rank in the Talent Search Examination (TSE) conducted by Nilachal Educational Trust in 10th class. \vspace{1mm}%

%\end {list2}

%______________________________________________________________________________________________________________________

    %  Extra Curricular
    \section{\mysidestyle Extra-Curricular Activities} 
\begin{list2}
\item Secured a position in top 6 in India the event Overnight, Algorithm intensive coding competition, certified by ACM, organised by Khsitij, 2013.   \vspace{1mm}%
\item Secured the $3^{rd}$ place in Nightshift , certified by IMechE organised by Khsitij, 2013.   \vspace{1mm}%
\item Part of ad-design team for the inter hall events of Azad hall. \vspace{1mm}%
\item Participated in Hack-You 2013 and 2012, organised by Yahoo.    \vspace{1mm}%
\item An active member of Kharagpur Robotix And Artificial Intelligence Society. \vspace{1mm}%
\item Participated in Robo-Soccer, 2010 organised by Robotix , IIT Kharagpur. \vspace{1mm}%
\item As a part of National Service Scheme in my sophomore year, taught the rural unpreviledged students and conducted cultural activities.\vspace{1mm}%
\item As a part of National Cadet Corps in my freshman year, learnt the skills of rifle firing, fire fighting.\vspace{1mm}%
\end{list2}


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

