%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Yogarshi Vyas
\documentclass[hidelinks,margin,line,10pt,a4paper]{resume}
\usepackage{hyperref}
\hypersetup{%
    pdfborder = {0 0 0}
}

%______________________________________________________________________________________________________________________
\begin{document}


\textbf{\begin{huge}\hspace{-28mm}Shashwat Kumar\end{huge}}	\hfill\vspace{0mm} C-327, Azad Hall
\vspace{0mm}\\\vspace{0mm}%
\hfill IIT Kharagpur
\vspace{0mm}\\\vspace{0mm}%
\hspace{-25mm}\hspace{-4mm} Senior Year Undergraduate Student, Roll Number - 10CS10041		\hfill West Bengal - 721302, India
\vspace{0mm}\\\vspace{0mm}%
\hspace{-25mm}\hspace{-4mm} Department of Computer Science and Engineering	\hfill Mobile: +91 8001060665
\vspace{0mm}\\\vspace{0mm}%
\hspace{-25mm} \hspace{-4mm}Indian Institute of Technology, Kharagpur \hfill Email : shashwatkmr.001@gmail.com


\begin{resume}
%__________________________________________________________________________________________________________________
% Education

\section{\mysidestyle Education}
%\vspace{5mm}%
\begin{list2}

            \item \textbf{Indian Institute of Technology, Kharagpur} \hfill Kharagpur, India \vspace{0mm}\\\vspace{1mm}%
    		Bachelor of Technology, Department of Computer Science and Engineering \hfill 2010 -- present  \vspace{-1mm}\\\vspace{1mm}%
		CGPA: 8.68/10 {(after 6 semesters)}
		 
             \item \textbf{Brij Bhushan Lal Public School} \hfill Bareilly, India \vspace{0mm}\\\vspace{1mm}%
    		{Class XII, Central Board of Secondary Education } \hfill { 2009}  \vspace{-1mm}\\\vspace{1mm}%
		{Performance: 88.00\%}
		
			\item \textbf{Brij Bhushan Lal Public School} \hfill Bareilly, India \vspace{0mm}\\\vspace{1mm}%
    		{Class X, Central Board of Secondary Education } \hfill { 2007 }  \vspace{-1mm}\\\vspace{1mm}%
		{Performance: 90.40\%}
% 


\end{list2}

    %__________________________________________________________________________________________________________________
    %  Relevant Coursework
    \section{\mysidestyle Relevant Courses} 
Algorithm I \& II, Image Processing, Computational Number Theory, Artificial Intelligence, Machine Learning, Advanced Graph Theory, Compilers, Operating Systems, Database Management Systems, Computer Networks, Software Engineering, Computer Organization and Architechture, Programming and Data Structures, Probability and Statistics and core mathematics and computer science courses.

    %__________________________________________________________________________________________________________________
    % Internship
    \section{\mysidestyle Summer Internship}


Title: \textbf{\emph{Integration of Payment Gateway }} \hfill May-July 2013 \\
Directi Internet Solutions, Mumbai, India \\
Mentor: Mr. Kirit Parmar
\vspace{2mm}%
\begin{itemize}
\item Integrated two payment gateways to reseller-end web interface of Directi using Java and JSP as server side technologies. First is an asynchronous payment gateway, \textbf{Alipay}, extensively used in China.
\item Second is a synchronous payment gateway, \textbf{PayU.in}, for Indian resellers.
\item The integration was tested and was successful after launching it on live servers.
\end{itemize}

    %__________________________________________________________________________________________________________________
    % Projects
    \section{\mysidestyle Projects}
    
Title: \textbf{\emph {Implementing Strategy layer for Robo-Soccer Environment }} \hfill July 2013 - Present \\ Indian Institute of Technology Kharagpur \hfill (Bachelor Thesis Project) \\
Guide: Prof. Jayanta Mukhopadhyay 
\vspace{2mm}%
\begin{itemize}
\item Working on development and design of strategy module for the small-sized wheeled robots to play soccer in dynamic environment.
\item Implementing Machine Learning techniques on strategy module for automated selection, execution and evaluation of most appropriate plays according to current state of the game.
\end{itemize}

Title: \textbf{\emph{Online Judge for Algorithmic Problems}} \hfill March - April 2013 \\
Indian Institute of Technology Kharagpur \hfill (Term Project) \\
Guide: Prof. Pabitra Mitra \\
Source: \href{https://github.com/shashwat001/evaluater}{https://github.com/shashwat001/evaluater}
\vspace{2mm}%
\begin{itemize}
\item Developed a web – based application in PHP/MySql for automated evaluation of computer programs written in C/C++. The application takes submission from user as a solution to some problem and complies and executes on local system and show the result to the user. The application also facilitates user to submit his own problem and participate in a contest.   
\end{itemize}

Title: \textbf{\emph{Facebook Timeline Search Application}}\hfill January - February 2013 \\
Indian Institute of Technology Kharagpur \hfill  (Term Project) \\
Guide: Prof. Pabitra Mitra
\vspace{2mm}%
\begin{itemize}
\item Development a web based application using \textbf{Facebook API} which provides search feature to user to search his facebook timeline. 
\item User can search posts, comments, likes, videos and photos for any particular word in any specific time period.
\end{itemize}

Title: \textbf{\emph{Online Mess Portal}}\hfill (Self Project) 
\vspace{2mm}%
\begin{itemize}
\item Developed an Online Mess Portal to for online functioning of Hostel Mess, such as choice filling of food items for a week, calculation of mess bills of all the residents etc.
\item The Portal was successfully implemented in Azad Hall in IIT Kharagpur among 700 residents.
\end{itemize}

\pagebreak

Title: \textbf{\emph{Time Management Software }} \hfill Feb-March 2012 \\
Indian Institute of Technology Kharagpur \hfill (Term Project)  \\
Guide: Prof. R. Mall
\vspace{2mm}%
\begin{itemize}
\item Developed Time management software with purpose for efficient time management for the executives of a company.
\item Applications involved registering daily appointment, scheduling meetings by finding common slots automatically and providing statistics of each executive such as total man-hours devoted to work and total meetings attended.
\end{itemize}




    %__________________________________________________________________________________________________________________
    %  Skills
    \section{\mysidestyle Skills} 

\begin{list2}
\item Operating Systems: Windows, Linux(Ubuntu)\vspace{1mm}%
\item Programming Languages: C, C++, Java, Python and PHP \vspace{1mm}%
\item Database Languages: SQL (SQLite, MySQL)\vspace{1mm}%
\item Development Environments: Netbeans, Codelite, Microsoft Visual Studio.\vspace{1mm}%
\end{list2}


    %__________________________________________________________________________________________________________________
    %  Positions of responsibility
    
\section{\mysidestyle Positions of Responsibility} 
\begin{list2}
\item	\textbf{Opensoft Captain}, Azad Hall of Residence for session 2013-2014.\vspace{1mm}%
\item \textbf{Artificial Intelligence Team head} of \textbf{Kharagpur RoboSoccer Student} Group (KRSSG), a student group working on a long-term project aiming to build autonomous soccer-playing robots with objective to participate in international RoboSoccer competitions FIRA and RoboCup.\vspace{1mm}%
\item 	 \textbf{General Secretary Web}, Azad Hall of Residence, IIT Kharagpur for the session 2012-2013.\vspace{1mm}%
\item 	Secretary Web, Azad Hall of Residence, IIT Kharagpur for session 2011-2012.\vspace{1mm}%
\begin{itemize}\vspace{-0.5em}
\renewcommand\labelitemi{--}
\item Responsible for initiation for online mess in hostel. \vspace{-0.5em}
\item Awarded Best Secretary of Azad Hall of Residence for the session Sep 2011 – Apr 2012.
\end{itemize}
\item Headed a workshop on developing robot to detect basic geometrical shapes through Image Processing in institute in Dec 2011.
\end{list2}

\section{\mysidestyle Awards and Achievements}
\begin {list2}
\item Member of one of the two Indian Teams to participate in \textbf{FIRA RoboSoccer World Cup} held in Malaysia in August 2013. Became first Indian team to win a match in FIRA World Cup.\vspace{1mm}%
\item One among two IIT Kharagpur teams to qualify for \textbf{ACM-ICPC Kharagpur regionals} in Dec 2012 and Amritapuri regionals in Oct 2013\vspace{1mm}%
\item Winner of Marauders Map, in Kshitij 2013, a coding event to design algorithm to optimize cost in an NP-Hard problem similar to Travelling Salesman Problem.\vspace{1mm}%
\item Won second prize in \textbf{Bitwise}, an online coding event organized by IIT Kharagpur in February 2012.\vspace{1mm}%
\item Won Bronze in ‘Negotiator’, an Artificial Intelligence coding event in Kshitij 2011, in which three codes have to negotiate with each other and maximize their profit.\vspace{1mm}%
\item Won Bronze in ‘Nuke Clear’ event in Kshitij 2012. It was a robotics event based on Image Processing in which a bot has to discovered bomb and avoids non-bomb objects by identifying shapes and colors of some objects and finally diffuses all the bombs.\vspace{1mm}%
\item \textbf{Ranked 12th} in India in \textbf{August Long Challenge}, an online programming competition, organized by Codechef in August 2012 and 10th in India in September 2013.\vspace{1mm}%
\item Won third place in Exebit 2013, an Online coding event organized by IIT Madras in February 2013.\vspace{1mm}%

\end {list2}

%______________________________________________________________________________________________________________________

    %  Extra Curricular
    \section{\mysidestyle Extra-Curricular Activities} 
\begin{list2}
\item Frequently participate in online algorithmic programming contests on Codechef , Codeforces and technological fests of Institutions.\vspace{1mm}%
\item Problem setter for Hackerrank and algorithmic online contests in institute. \vspace{1mm}%
\item Part of Athletics team under NSO (National Sports Organization). \vspace{1mm}%
\end{list2}


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

